Internship Summary: Mid-Term Review

### 2020-07-31 RapportStage/Rapport.tex
get rid of wrapfig

\begin{wrapfigure}{R}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{TopologyEP.pdf}
    \caption{A generic EP with the square-root branch point topology. A loop around the EP interconvert the states.}
    \label{fig:TopologyEP}
\end{wrapfigure}
By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.3\textwidth]{2x2.pdf}
    \hspace{0.2\textwidth}
    \includegraphics[width=0.3\textwidth]{i2x2.pdf}
    \caption{Energies, as given by Eq.~\ref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
    \label{fig:2x2}
\end{figure}

@@

\begin{table}[h!]
    \centering
    \caption{Percentage of electron correlation energy recovered and $\expval*{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from Ref.~\cite{Gill_1988}).}
    \begin{tabular}{ccccccc}
\hline
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval*{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\hline
\end{tabular}
    \label{tab:SpinContamination}
\end{table}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{Nedivergence.png}
    \includegraphics[width=0.45\textwidth]{HFdivergence.png}
    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from Ref.~\cite{Olsen_1996}).}
    \label{fig:NeHFDiv}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{RHF and sb-UHF energies in the minimal basis and exact energies (in the complete basis) for various $R$.}
\begin{tabular}{ccccccccc}
\hline
\hline
$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
\hline
RHF 	& 10.00000 & 1.000000 & 0.500000 & 0.333333 & 0.200000 & 0.100000 & 0.010000 & 0.001000 \\
UHF 	& 10.00000 & 1.000000 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
Exact 	& 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
\hline
\hline
\end{tabular}
\label{tab:ERHFvsEUHF}
\end{table}

\begin{wrapfigure}{R}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{EsbHF.pdf}
    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
    \label{fig:SpheriumNrj}
\end{wrapfigure}

@@

In this subsection, we investigate how \titou{parameters} of $\hH(\lambda)$ influence the radius of convergence of the perturbation series. Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$. Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series. To find them we solve simultaneously the following equations:
\begin{subequations}
\begin{align}
	\label{eq:PolChar}
	\det[E\hI-\hH(\lambda)] & = 0,
	\\ 
	\label{eq:DPolChar}
	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
\end{align}
\end{subequations}
where $\hI$ is the identity operator.
Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system. If an energy is also solution of Eq.~\eqref{eq:DPolChar} then this energy is degenerate. In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate. These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.

@@

\begin{wrapfigure}{R}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
    \label{fig:RHFMiniBas}
\end{wrapfigure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{PartitioningRCV2.pdf}
    \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
    \label{fig:RadiusPartitioning}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{MPlargebasis.pdf}
    \includegraphics[width=0.45\textwidth]{WCElargebasis.pdf}
    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
    \label{fig:RadiusBasis}
\end{figure}

\begin{table}[h!]
\centering
\footnotesize
\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
\begin{tabular}{cccccccc}
\hline
\hline
$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
\hline
MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
\hline
\hline
\end{tabular}
\label{tab:SingAlpha}
\end{table}

@@

\begin{wrapfigure}{R}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
    \label{fig:UHFMiniBas}
\end{wrapfigure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
    \label{fig:UHFEP}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
    \caption{\centering Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
    \label{fig:UHFPT}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{TopologyEP.pdf}
    \caption{A generic EP with the square-root branch point topology. A loop around the EP interconvert the states.}
    \label{fig:TopologyEP}
\end{figure}
By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.3\textwidth]{2x2.pdf}
    \hspace{0.2\textwidth}
    \includegraphics[width=0.3\textwidth]{i2x2.pdf}
    \caption{Energies, as given by Eq.~\ref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
    \label{fig:2x2}
\end{figure}

@@

\begin{table}
    \centering
    \caption{Percentage of electron correlation energy recovered and $\expval*{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from Ref.~\cite{Gill_1988}).}
    \begin{tabular}{ccccccc}
\hline
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval*{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\hline
\end{tabular}
    \label{tab:SpinContamination}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{Nedivergence.png}
    \includegraphics[width=0.45\textwidth]{HFdivergence.png}
    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from Ref.~\cite{Olsen_1996}).}
    \label{fig:NeHFDiv}
\end{figure}

@@

\begin{table}
\centering
\caption{RHF and sb-UHF energies in the minimal basis and exact energies (in the complete basis) for various $R$.}
\begin{tabular}{ccccccccc}
\hline
\hline
$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
\hline
RHF 	& 10.00000 & 1.000000 & 0.500000 & 0.333333 & 0.200000 & 0.100000 & 0.010000 & 0.001000 \\
UHF 	& 10.00000 & 1.000000 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
Exact 	& 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
\hline
\hline
\end{tabular}
\label{tab:ERHFvsEUHF}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{EsbHF.pdf}
    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
    \label{fig:SpheriumNrj}
\end{figure}

@@

In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series. Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$. Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series. To find them we solve simultaneously the following equations:
\begin{subequations}
\begin{align}
	\label{eq:PolChar}
	\det[E\hI-\hH(\lambda)] & = 0,
	\\ 
	\label{eq:DPolChar}
	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
\end{align}
\end{subequations}
where $\hI$ is the identity operator.
Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system. If an energy is also solution of Eq.~\eqref{eq:DPolChar} then this energy is degenerate. In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate. These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{EMP_RHF_R10.pdf}
    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
    \label{fig:RHFMiniBas}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
    \label{fig:RadiusPartitioning}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
    \label{fig:RadiusBasis}
\end{figure}

\begin{table}
\centering
\footnotesize
\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
\begin{tabular}{cccccccc}
\hline
\hline
$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
\hline
MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
\hline
\hline
\end{tabular}
\label{tab:SingAlpha}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{EMP_UHF_R10.pdf}
    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
    \label{fig:UHFMiniBas}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
    \label{fig:UHFEP}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
    \caption{\centering Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
    \label{fig:UHFPT}
\end{figure}
